Mealtime conversations between parents and their 2-year-old children in five cultural contexts

### 2022-11-22 manuscript/paper.Rmd
add paper

abstract: |
  Children all over the world learn language, yet, the context in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). We found a comparable pattern of communicative interactions across cultural settings, which were attenuated in ways that likely reflect local norms and values. These results suggest that children can rely on similarly structured communicative environments and will inform theories of language learning.

@@

Children learn language in interactions with language-competent others [@clark2009first; @tomasello2009constructing; @bruner1983child; @levinson2014origin; @bohn2019pervasive].Explaining how children accomplish this feat poses a serious challenge because social interactions between children and their social partners are structured by norms, values, and beliefs that vary across cultural and historical contexts [@rogoff2003cultural]. As a consequence, children may encounter dramatically different language learning environments. Yet, the fact that children usually achieve fluency in their local language(s) suggests that they use a suite of compensatory learning strategies to adapt flexibly to their respective learning environment [@rowe2020language; @cristia2022systematic; @kidd2022diverse]. Detailed documentation of learning environments across cultural contexts is needed to inform theorizing about children’s learning processes. In this paper, we contribute to this effort by reporting on cross-cultural variation in parent-child communicative interactions in a semi-structured setting: meals involving parents and their 2-year-old child.

@@

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions [@broesch2022roadmap]. Work in Western-affluent settings has shown that the amount of language input children receive varies substantially across routine activities. For example, @soderstrom2013caregivers found that Canadian adults spoke most during book reading and structured playtime [see also @tamis2019routine]. Such activities, however, are very specific to Western, affluent settings and less frequent or absent in other cultural contexts. A particularly promising context for cross-cultural research appears to be mealtimes: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs [@ochs2006cultural; @fjellstrom2004mealtime; @blum2012dinner; @koester2022parental]. Furthermore, mealtimes have been a fruitful context for studying caregiver-child communication in a Western context, for example, in the U.S. [e.g., @beals1993explanatory; @beals1997sources; @snow2006mealtime].

@@

The goal of this study was to compare communicative interactions between parents and their children during mealtime across diverse cultural settings. We aimed for a naturalistic but comparable setup by a) asking families to record in their homes, b) recruiting families with children between 2 and 3 years of age and c) focusing on 10-minute-long episodes during which all three family members (mother, father, child) were present. Even though the constellation of two parents and one child might be less representative of the overall family demographics in some settings, it allowed us to directly quantify and compare communicative interactions. We obtained recordings from five different cultural settings, including families living in the Global South and North, as well as in urban and rural settings: the city of Buenos Aires, Argentina, small villages in the Apeú region, Brazil, small villages close to Cotacachi, Ecuador, the city of Münster, Germany, and the city of Kyoto, Japan.

@@

The final sample consisted of `r sum(dem$n)` families from five cultural contexts. This included `r dem%>%filter(country == "Argentina")%>%pull(n)` families from the city of Buenos Aires, Argentina (urban setting), `r dem%>%filter(country == "Brazil")%>%pull(n)` families from villages in the Amazon region near Apeú, Brazil (rural setting), `r dem%>%filter(country == "Ecuador")%>%pull(n)` from villages near Cotacachi, Ecuador (rural setting), `r dem%>%filter(country == "Germany")%>%pull(n)` families from the city of Münster, Germany (urban setting) and `r dem%>%filter(country == "Japan")%>%pull(n)` families from the city of Kyoto, Japan (urban setting). For the recording sessions, all families comprised a father, a mother and a child aged between 2 years and 3 years, 2 months. Some videos partly included additional children (n = 1 for Argentina, Brazil and Ecuador).

@@

Families lived in villages with 800-5,000 inhabitants located within 1 hour (by car) of the city of Cotacachi in the Imbabura province. They were recruited via personal contacts mediated by the community president. The family language was Ecuadorian Spanish with elements of Kichwa. Compensation included food (e.g., rice or oat) and USD 4. Most parents had completed primary school (~10 years of schooling, mothers: 50%; fathers: 56%). Mothers worked mainly as housewives (59%) while fathers engaged in paid labor (77%). Around 40% of children were looked after by a person other than the mother during the day.

@@

The model comparison clearly favored the interaction model assuming that the difference in length of themes for each pair of interlocutors varied across cultural settings cultural setting (WAIC = `r comp_length%>%filter(model == "bm7_3")%>%pull(waic)`, se = `r comp_length%>%filter(model == "bm7_3")%>%pull(se_waic)`, weight = `r comp_length%>%filter(model == "bm7_3")%>%pull(weight)`; second best model (without interaction): WAIC = `r comp_length%>%filter(model == "bm7_2")%>%pull(waic)`, se = `r comp_length%>%filter(model == "bm7_2")%>%pull(se_waic)`, weight = `r comp_length%>%filter(model == "bm7_2")%>%pull(weight)`). The average predicted length of a theme across interlocutors and settings was `r fix_bm7_3%>%pull(Estimate)` rounds [95%CrI = `r fix_bm7_3%>%pull(Q2.5)` - `r fix_bm7_3%>%pull(Q97.5)`]. Figure \@ref(fig:fig3)C indicates a variable pattern across cultural settings. In Japan, themes were approximately equally long for all pairs of interlocutors. In the other settings, conversations between mother and father were shorter compared to conversations between one of the parents and the child. This pattern was less pronounced in Ecuador compared to Germany, Brazil and Argentina. Overall, themes lasted slightly longer in Brazil compared to the other settings.

@@

Families from Brazil and Ecuador had longer periods of silences and produced fewer gestures. This mirrors results by @cristia2022systematic who synthesized 29 studies on naturalistic language input and found that infants growing up in rural settings heard less child-directed speech compared to children growing up in urban settings. For rural Ecuador, @parga2010puerilizado reports a norm that meals are supposed to be taken in silence and only the highest authority (usually the father) is allowed to speak. In our sample, such norms seemed to have influenced mothers’ communication the most: there was less talk by mothers in Ecuador compared to the other settings (except Brazil) while the amount of talk by fathers and children was relatively similar. However, when comparing absolute numbers across settings, it is worth pointing out that this norm -- at least in the present study -- mainly had an attenuating effect. Fathers in all settings were the least likely to initiate a theme even though the cultural norm in Ecuador designates them as the most active communicator.

@@

Furthermore, our sample was a convenience sample in that we relied on established contacts and collaborations to recruit families in different settings. As such, the grouping into rural and urban contexts is confounded with the normative belief systems of particular regions. Thus, we do not think that living in a rural setting per se affects communicative interactions in a systematic way but the specific cultural norms and practices associated with rural subsistence produced the patterns we observed.

@@

Our findings offer important insights into how children’s language learning environments vary across diverse cultural settings. For all aspects of communication we investigated in the current study, a common pattern emerged across cultural settings suggesting that children can rely on similar information sources and learning processes. This common pattern was attenuated in some of the settings in a way that likely reflected particular local norms, values and beliefs and ecologies. This exemplifies the importance of quantitative cross-cultural research for theory building in language acquisition.

>>>>

abstract: |
  Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). We found a comparable pattern of communicative interactions across cultural settings, which were attenuated in ways that likely reflect local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.

@@

Children learn language in interactions with language-competent others [@clark2009first; @tomasello2009constructing; @bruner1983child; @levinson2014origin; @bohn2019pervasive]. Social interactions between children and their social partners are structured by norms, values, and beliefs that vary substantially across cultural and historical contexts [@rogoff2003cultural]. As a consequence, children may encounter dramatically different language learning environments. Yet, the fact that children usually achieve fluency in their local language(s) suggests that they use a suite of compensatory learning strategies to adapt flexibly to their respective learning environment [@rowe2020language; @cristia2022systematic; @kidd2022diverse]. Explaining how children accomplish this feat poses a serious theoretical and empirical challenge. Detailed documentation of learning environments across cultural contexts is needed to inform theorizing about children’s learning processes. In this paper, we contribute to this effort by reporting on cross-cultural variation in parent-child communicative interactions in a semi-structured setting: meals involving parents and their 2-year-old child.

@@

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions [@broesch2022roadmap]. Prior work has shown that the amount of language input children receive varies substantially across routine activities. For example, @soderstrom2013caregivers found that Canadian adults spoke most during book reading and structured playtime [see also @tamis2019routine]. Such activities, however, are very specific to industrialized societies and less frequent or absent in other cultural contexts. A cross-culturally recurrent, and hence particularly promising, context for cross-cultural research is mealtime: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs [@ochs2006cultural; @fjellstrom2004mealtime; @blum2012dinner; @koester2022parental]. Furthermore, mealtimes have been a fruitful context for studying caregiver-child communication, for example, in the U.S. [e.g., @beals1993explanatory; @beals1997sources; @snow2006mealtime].

@@

The goal of this study was to compare communicative interactions between parents and their children during mealtime across diverse cultural settings. We aimed for a naturalistic but comparable setup by a) asking families to record in their homes, b) recruiting families with a single -- usually the first -- child between 2 and 3 years of age and c) focusing on 10-minute-long episodes during which three family members (mother, father, one child) were present. Even though the constellation of two parents and one child might be less representative of the overall family demographics in some settings, it allowed us to directly quantify and compare communicative interactions. We obtained recordings from five different cultural settings, including families living in the Global South and North, as well as in urban and rural settings: the city of Buenos Aires, Argentina, small villages in the Apeú region, Brazil, small villages close to Cotacachi, Ecuador, the city of Münster, Germany, and the city of Kyoto, Japan.

@@

The final sample consisted of `r sum(dem$n)` families from five cultural contexts. This included `r dem%>%filter(country == "Argentina")%>%pull(n)` families from the city of Buenos Aires, Argentina (urban setting), `r dem%>%filter(country == "Brazil")%>%pull(n)` families from villages in the Amazon region near Apeú, Brazil (rural setting), `r dem%>%filter(country == "Ecuador")%>%pull(n)` from villages near Cotacachi, Ecuador (rural setting), `r dem%>%filter(country == "Germany")%>%pull(n)` families from the city of Münster, Germany (urban setting) and `r dem%>%filter(country == "Japan")%>%pull(n)` families from the city of Kyoto, Japan (urban setting). For the recording sessions, all families comprised a father, a mother and a child aged between 2 years and 3 years, 2 months. Almost all children were the first child in the family. Some videos partly included additional children (n = 1 for Argentina, Brazil and Ecuador).

@@

Families identified as belonging to the Kichwa community and lived in villages with 800-5,000 inhabitants located within 1 hour (by car) of the city of Cotacachi in the Imbabura province. They were recruited via personal contacts mediated by the community president. The family language was Ecuadorian Spanish with elements of Kichwa. Compensation included food (e.g., rice or oat) and USD 4. Most parents had completed primary school (~10 years of schooling, mothers: 50%; fathers: 56%). Mothers worked mainly as housewives (59%) while fathers engaged in paid labor (77%). Around 40% of children were looked after by a person other than the mother during the day.

@@

The model comparison clearly favored the interaction model assuming that the difference in length of themes for each pair of interlocutors varied across cultural settings (WAIC = `r comp_length%>%filter(model == "bm7_3")%>%pull(waic)`, se = `r comp_length%>%filter(model == "bm7_3")%>%pull(se_waic)`, weight = `r comp_length%>%filter(model == "bm7_3")%>%pull(weight)`; second best model (without interaction): WAIC = `r comp_length%>%filter(model == "bm7_2")%>%pull(waic)`, se = `r comp_length%>%filter(model == "bm7_2")%>%pull(se_waic)`, weight = `r comp_length%>%filter(model == "bm7_2")%>%pull(weight)`). The average predicted length of a theme across interlocutors and settings was `r fix_bm7_3%>%pull(Estimate)` rounds [95%CrI = `r fix_bm7_3%>%pull(Q2.5)` - `r fix_bm7_3%>%pull(Q97.5)`]. Figure \@ref(fig:fig3)C indicates a variable pattern across cultural settings. In Japan, themes were approximately equally long for all pairs of interlocutors. In the other settings, conversations between mother and father were shorter compared to conversations between one of the parents and the child. This pattern was less pronounced in Ecuador compared to Germany, Brazil and Argentina. Overall, themes lasted slightly longer in Brazil compared to the other settings.

@@

Families from Brazil and Ecuador had longer periods of silences and produced fewer gestures. This mirrors results by @cristia2022systematic who synthesized 29 studies on naturalistic language input and found that infants growing up in rural settings heard less child-directed speech compared to children growing up in urban settings. For the Kichwa community in Ecuador, @sanchez2010oficio reports a norm that meals are supposed to be taken in silence. In our sample, such norms seemed to have influenced mothers’ communication the most: there was less talk by mothers in Ecuador compared to the other settings (except Brazil), while the amount of talk by fathers and children was relatively similar. However, given that all family members talked, it is worth pointing out that this norm -- at least in the present study -- mainly had an attenuating effect.

@@

Furthermore, our sample was a convenience sample in that we relied on established contacts and collaborations to recruit families in different settings. As such, the grouping into rural and urban contexts is confounded with the normative belief systems of particular regions. Thus, we do not think that living in a rural setting per se affects communicative interactions in a systematic way but the specific cultural norms and practices associated with rural subsistence in these settings produced the patterns we observed. Future work should combine our quantitative approach with a qualitative assessment of the local norms surrounding communication and mealtime to better understand the link between norms, values and beliefs and communicative behavior.

@@

Our findings offer important insights into the variable and constant aspects of children’s language learning environments across diverse cultural settings. For all aspects of communication we investigated in the current study, a common pattern emerged across cultural settings suggesting that children can rely on similar information sources and learning processes. This common pattern was attenuated in some of the settings in a way that likely reflected particular local norms, values, beliefs and ecologies. This exemplifies the importance of quantitative cross-cultural research for theory building in language acquisition.

### 2022-11-22 manuscript/paper.tex
add paper

\abstract{%
Children all over the world learn language, yet, the context in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). We found a comparable pattern of communicative interactions across cultural settings, which were attenuated in ways that likely reflect local norms and values. These results suggest that children can rely on similarly structured communicative environments and will inform theories of language learning.
}

@@

Children learn language in interactions with language-competent others (Bohn \& Frank, 2019; Bruner, 1983; Clark, 2009; Levinson \& Holler, 2014; Tomasello, 2009).Explaining how children accomplish this feat poses a serious challenge because social interactions between children and their social partners are structured by norms, values, and beliefs that vary across cultural and historical contexts (Rogoff et al., 2003). As a consequence, children may encounter dramatically different language learning environments. Yet, the fact that children usually achieve fluency in their local language(s) suggests that they use a suite of compensatory learning strategies to adapt flexibly to their respective learning environment (Cristia, 2022; Kidd \& Garcia, 2022; Rowe \& Weisleder, 2020). Detailed documentation of learning environments across cultural contexts is needed to inform theorizing about children's learning processes. In this paper, we contribute to this effort by reporting on cross-cultural variation in parent-child communicative interactions in a semi-structured setting: meals involving parents and their 2-year-old child.

@@

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions (Broesch, Lew-Levy, Kärtner, Kanngiesser, \& Kline, 2022). Work in Western-affluent settings has shown that the amount of language input children receive varies substantially across routine activities. For example, Soderstrom and Wittebolle (2013) found that Canadian adults spoke most during book reading and structured playtime (see also Tamis-LeMonda, Custode, Kuchirko, Escobar, \& Lo, 2019). Such activities, however, are very specific to Western, affluent settings and less frequent or absent in other cultural contexts. A particularly promising context for cross-cultural research appears to be mealtimes: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs (Blum-Kulka, 2012; Fjellström, 2004; Köster et al., 2022; Ochs \& Shohet, 2006). Furthermore, mealtimes have been a fruitful context for studying caregiver-child communication in a Western context, for example, in the U.S. (e.g., Beals, 1993, 1997; Snow \& Beals, 2006).

@@

The final sample consisted of 99 families from five cultural contexts. This included 20 families from the city of Buenos Aires, Argentina (urban setting), 18 families from villages in the Amazon region near Apeú, Brazil (rural setting), 13 from villages near Cotacachi, Ecuador (rural setting), 24 families from the city of Münster, Germany (urban setting) and 24 families from the city of Kyoto, Japan (urban setting). For the recording sessions, all families comprised a father, a mother and a child aged between 2 years and 3 years, 2 months. Some videos partly included additional children (n = 1 for Argentina, Brazil and Ecuador).

@@

Families lived in villages with 800-5,000 inhabitants located within 1 hour (by car) of the city of Cotacachi in the Imbabura province. They were recruited via personal contacts mediated by the community president. The family language was Ecuadorian Spanish with elements of Kichwa. Compensation included food (e.g., rice or oat) and USD 4. Most parents had completed primary school (\textasciitilde10 years of schooling, mothers: 50\%; fathers: 56\%). Mothers worked mainly as housewives (59\%) while fathers engaged in paid labor (77\%). Around 40\% of children were looked after by a person other than the mother during the day.

@@

The model comparison clearly favored the interaction model assuming that the difference in length of themes for each pair of interlocutors varied across cultural settings cultural setting (WAIC = 11657.48, se = 106.30, weight = 1.00; second best model (without interaction): WAIC = 11671.33, se = 106.59, weight = 0.00). The average predicted length of a theme across interlocutors and settings was 5.71 rounds {[}95\%CrI = 3.95 - 8.35{]}. Figure \ref{fig:fig3}C indicates a variable pattern across cultural settings. In Japan, themes were approximately equally long for all pairs of interlocutors. In the other settings, conversations between mother and father were shorter compared to conversations between one of the parents and the child. This pattern was less pronounced in Ecuador compared to Germany, Brazil and Argentina. Overall, themes lasted slightly longer in Brazil compared to the other settings.

@@

Families from Brazil and Ecuador had longer periods of silences and produced fewer gestures. This mirrors results by Cristia (2022) who synthesized 29 studies on naturalistic language input and found that infants growing up in rural settings heard less child-directed speech compared to children growing up in urban settings. For rural Ecuador, Parga (2010) reports a norm that meals are supposed to be taken in silence and only the highest authority (usually the father) is allowed to speak. In our sample, such norms seemed to have influenced mothers' communication the most: there was less talk by mothers in Ecuador compared to the other settings (except Brazil) while the amount of talk by fathers and children was relatively similar. However, when comparing absolute numbers across settings, it is worth pointing out that this norm -- at least in the present study -- mainly had an attenuating effect. Fathers in all settings were the least likely to initiate a theme even though the cultural norm in Ecuador designates them as the most active communicator.

@@

Our findings offer important insights into how children's language learning environments vary across diverse cultural settings. For all aspects of communication we investigated in the current study, a common pattern emerged across cultural settings suggesting that children can rely on similar information sources and learning processes. This common pattern was attenuated in some of the settings in a way that likely reflected particular local norms, values and beliefs and ecologies. This exemplifies the importance of quantitative cross-cultural research for theory building in language acquisition.

@@

\leavevmode\vadjust pre{\hypertarget{ref-parga2010puerilizado}{}}%
Parga, J. S. (2010). Puerilizado y adulterado: Representaciones institucionales de la infancia. \emph{Universitas-XXI, Revista de Ciencias Sociales y Humanas}, (13), 95--130.

@@

>>>>

\abstract{%
Children all over the world learn language, yet, the contexts in which they do so varies substantially. This variation needs to be systematically quantified to build robust and generalizable theories of language acquisition. We compared communicative interactions between parents and their two-year-old children (N = 99 families) during mealtime across five cultural settings (Brazil, Ecuador, Argentina, Germany, Japan) and coded the amount of talk and gestures as well as their conversational embedding (interlocutors, speech acts, themes). We found a comparable pattern of communicative interactions across cultural settings, which were attenuated in ways that likely reflect local norms and values. These results suggest that children encounter similarly structured communicative environments across diverse cultural contexts and will inform theories of language learning.
}

@@

Children learn language in interactions with language-competent others (Bohn \& Frank, 2019; Bruner, 1983; Clark, 2009; Levinson \& Holler, 2014; Tomasello, 2009). Social interactions between children and their social partners are structured by norms, values, and beliefs that vary substantially across cultural and historical contexts (Rogoff et al., 2003). As a consequence, children may encounter dramatically different language learning environments. Yet, the fact that children usually achieve fluency in their local language(s) suggests that they use a suite of compensatory learning strategies to adapt flexibly to their respective learning environment (Cristia, 2022; Kidd \& Garcia, 2022; Rowe \& Weisleder, 2020). Explaining how children accomplish this feat poses a serious theoretical and empirical challenge. Detailed documentation of learning environments across cultural contexts is needed to inform theorizing about children's learning processes. In this paper, we contribute to this effort by reporting on cross-cultural variation in parent-child communicative interactions in a semi-structured setting: meals involving parents and their 2-year-old child.

@@

One of the challenges of cross-cultural work lies in selecting an appropriate context for comparing the structure of communicative interactions (Broesch, Lew-Levy, Kärtner, Kanngiesser, \& Kline, 2022). Prior work has shown that the amount of language input children receive varies substantially across routine activities. For example, Soderstrom and Wittebolle (2013) found that Canadian adults spoke most during book reading and structured playtime (see also Tamis-LeMonda, Custode, Kuchirko, Escobar, \& Lo, 2019). Such activities, however, are very specific to industrialized societies and less frequent or absent in other cultural contexts. A cross-culturally recurrent, and hence particularly promising, context for cross-cultural research is mealtime: across societies, meals are social events that are structured by -- and used to transmit -- cultural norms, values and beliefs (Blum-Kulka, 2012; Fjellström, 2004; Köster et al., 2022; Ochs \& Shohet, 2006). Furthermore, mealtimes have been a fruitful context for studying caregiver-child communication, for example, in the U.S. (e.g., Beals, 1993, 1997; Snow \& Beals, 2006).

@@

The final sample consisted of 99 families from five cultural contexts. This included 20 families from the city of Buenos Aires, Argentina (urban setting), 18 families from villages in the Amazon region near Apeú, Brazil (rural setting), 13 from villages near Cotacachi, Ecuador (rural setting), 24 families from the city of Münster, Germany (urban setting) and 24 families from the city of Kyoto, Japan (urban setting). For the recording sessions, all families comprised a father, a mother and a child aged between 2 years and 3 years, 2 months. Almost all children were the first child in the family. Some videos partly included additional children (n = 1 for Argentina, Brazil and Ecuador).

@@

Families identified as belonging to the Kichwa community and lived in villages with 800-5,000 inhabitants located within 1 hour (by car) of the city of Cotacachi in the Imbabura province. They were recruited via personal contacts mediated by the community president. The family language was Ecuadorian Spanish with elements of Kichwa. Compensation included food (e.g., rice or oat) and USD 4. Most parents had completed primary school (\textasciitilde10 years of schooling, mothers: 50\%; fathers: 56\%). Mothers worked mainly as housewives (59\%) while fathers engaged in paid labor (77\%). Around 40\% of children were looked after by a person other than the mother during the day.

@@

The model comparison clearly favored the interaction model assuming that the difference in length of themes for each pair of interlocutors varied across cultural settings (WAIC = 11657.48, se = 106.30, weight = 1.00; second best model (without interaction): WAIC = 11671.33, se = 106.59, weight = 0.00). The average predicted length of a theme across interlocutors and settings was 5.71 rounds {[}95\%CrI = 3.95 - 8.35{]}. Figure \ref{fig:fig3}C indicates a variable pattern across cultural settings. In Japan, themes were approximately equally long for all pairs of interlocutors. In the other settings, conversations between mother and father were shorter compared to conversations between one of the parents and the child. This pattern was less pronounced in Ecuador compared to Germany, Brazil and Argentina. Overall, themes lasted slightly longer in Brazil compared to the other settings.

@@

Families from Brazil and Ecuador had longer periods of silences and produced fewer gestures. This mirrors results by Cristia (2022) who synthesized 29 studies on naturalistic language input and found that infants growing up in rural settings heard less child-directed speech compared to children growing up in urban settings. For the Kichwa community in Ecuador, Sánchez-Parga (2010) reports a norm that meals are supposed to be taken in silence. In our sample, such norms seemed to have influenced mothers' communication the most: there was less talk by mothers in Ecuador compared to the other settings (except Brazil), while the amount of talk by fathers and children was relatively similar. However, given that all family members talked, it is worth pointing out that this norm -- at least in the present study -- mainly had an attenuating effect.

@@

Our findings offer important insights into the variable and constant aspects of children's language learning environments across diverse cultural settings. For all aspects of communication we investigated in the current study, a common pattern emerged across cultural settings suggesting that children can rely on similar information sources and learning processes. This common pattern was attenuated in some of the settings in a way that likely reflected particular local norms, values, beliefs and ecologies. This exemplifies the importance of quantitative cross-cultural research for theory building in language acquisition.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-sanchez2010oficio}{}}%
Sánchez-Parga, J. (2010). \emph{El oficio de antrop{ó}logo. Cr{í}ticia de la raz{ó}n (inter) cultural.} Ediciones Abya-Yala, Quito.
